---
title: "hw4.Rmd"
author: "Seydou Yacouba"
date: "March 6, 2019"
output: html_document
---

```{r}
library(datasets)
library(ggplot2)
library(dplyr)
str(ChickWeight)
head(ChickWeight)
```

#1
```{r}
weight0 <- knitr::kable(
  ChickWeight %>%
  group_by(Diet) %>%
  summarise(chick_freq = n(),
            average_weight = mean(weight),
            sd_weight = sd(weight)))
weight0
```

#2
```{r}
complete <- ChickWeight %>% 
              group_by(Chick) %>% 
              filter(n() == 12)


knitr::kable(head(complete))
complete[1:3,]
```
#3
```{r}
weightgain <- complete %>%
              group_by(Chick) %>%
              mutate(weightgain = c(NA,diff(weight)))
knitr::kable(head(complete))
weightgain
weightgain[1:3,]
```
#4

```{r}
weightgain %>%  ungroup(Chick)%>%
  filter(Time == 21) %>%
  mutate(Diet = reorder(Diet,weightgain, median))%>%
  ggplot(aes(x = Diet, y = weightgain, color = Diet)) +
  geom_boxplot() + 
  ggtitle("Boxplots of Weightgain by Diet for 21 Days")
```

The meidan for `Diet 1`  and `Diet 4` is almost close. You can see that ther are more weight gain in with `Diet 2`(above the median).There is an outlier that shows a major agin loss for `Diet 3`.`Diet 4` also has an outlier for heavy wight gain.

#5
```{r}
#numberic
weightgain %>%
group_by(Chick, Diet) %>%
    summarise(Total = sum(weightgain, na.rm = TRUE)) %>%
    ungroup() %>%
    filter(Total %in% c(min(Total), max(Total)))

```
```{r}
#graphical
weightgain %>%
group_by(Chick, Diet) %>%
    summarise(Total = sum(weightgain, na.rm = TRUE)) %>%
    ungroup() %>%
    filter(Total %in% c(min(Total), max(Total))) %>%
    ggplot(aes(x=Chick, y=Total, fill=Diet)) + geom_col()
```

35 gain the most weight with diet 3, and 24 lost the most weight with diet 2.

#6
```{r}
chick_min <- min(complete$weight)
chick_max <- max(complete$weight)
chick <- complete %>%
    group_by(Chick) %>%
    filter(Time == 0, weight %in% c(chick_min, chick_max)) %>%
select(Chick)
complete %>%
group_by(Chick) %>%
    filter(Chick %in% chick$Chick) %>%
    ggplot(aes(Time, weight, color=Chick)) + 
               geom_line()
```

#7
what i found really intersting in the datset is that i can see how each diet work during the 21 days. so i can chose a specific diet that works better for the chicks to improve their weight gain.
